\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Application

### 2018-08-24 paper/paper.tex
title

\title{
  % \includegraphics[width=0.2\textwidth]{hpi_logo_2017}\\
  \vspace{24pt}
  In-Memory Trajectory Analysis on Taxi Data
}
\subtitle{
  Seminar Trends and Concepts 3\\
  Summer Semester 2018
}

@@

\author{
  Marcel Jankrift\\
  Sebastian Kliem\\
  Toni Stachewicz\\[12pt]
  Supervisors:\\
  Dr. Matthias Uflacker, Keven Richly
}

>>>>

\title{
  % \includegraphics[width=0.2\textwidth]{hpi_logo_2017}\\
  \vspace{24pt}
  % In-Memory Trajectory Analysis on Taxi Data
  Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Application
}
\subtitle{
  Seminar Trends and Concepts 3\\
  Summer Semester 2018
}

@@

\author{
  Marcel Jankrift, Sebastian Kliem, Toni Stachewicz\\[12pt]
  Supervisors:\\
  Dr. Matthias Uflacker, Keven Richly
}
